Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-30 paper.tex
Updated Proposal
Work in progress.

        \subsubsection{Birth} Birth is the first process of our algorithm, and it is
        responsible for the initial generation of individuals. This algorithm starts
        with a randomly generated population.

>>>>

        \subsubsection{Birth} Birth is the first step of the population's
        evolution. For the algorithm representation, we begin with the
        generation of a randomly set of individuals.
